\section{Robustness and Failure Audit}

\subsection{Predefined diagnostic gates}

We distinguish source-direction checks from robust replication. The primary sample can
pass a directional check---reversal loses slightly less than momentum in Q4---while
failing every stability condition needed for a usable router.

\begin{table}[H]
\centering
\caption{Robust replication diagnostics}
\label{tab:gates}
\begin{tabularx}{\textwidth}{YcY}
\toprule
Diagnostic & Passed & Interpretation \\
\midrule
Primary Q4 reversal mean is positive & No & Replacement sleeve still loses in Q4 \\
Primary Q4 reversal wins at least half of months & No & Wins in 4 of 14 months \\
Primary router increment has HAC $t\geq 1$ & No & Increment $t=0.06$ \\
Equal-proxy Q4 reversal exceeds momentum & No & Q4 ranking reverses \\
Equal-proxy router exceeds momentum & No & Router endpoint is lower \\
Positive increment is broad across time & No & One event determines the sign \\
\bottomrule
\end{tabularx}
\end{table}

The failure is overdetermined: it does not rest on one conventional significance cutoff.
It appears in sign stability, win frequency, event influence, market-proxy sensitivity,
and benchmark ranking.

\subsection{Why no percentile search follows}

It would be straightforward to search for a volatility percentile at which the primary
sample looks better. Such a search would answer a different question. The source paper's
75th-percentile rule was the object of replication; the current evidence indicates that
volatility does not impose a stable ordering on the sleeves. Optimizing a boundary on a
non-monotonic and proxy-sensitive relation would primarily fit the locations of a small
number of events.

For the same reason, we do not remove products or sectors based on historical
contribution. Outcome-based universe reduction would change the cross-market replication
into a strategy-selection exercise and understate specification uncertainty.

\subsection{Indicative implementation evidence}

An indicative implementation check applied product-specific fee conventions and uniform
adverse slippage. It did not change the economic ranking between the primary router and
momentum. The difference remained small relative to model and path uncertainty. We do
not report execution parameters or interpret this translation as a fully implementable
portfolio: it excludes integer-lot positioning, capacity, exchange-limit, and margin
models. Detailed execution research is unnecessary until the gross mechanism is stable.
