\section{Public Evidence Contract}

\subsection{Sanitization boundary}

The manuscript and all five figures build from a single reviewed JSON file containing
rounded aggregate statistics. The public evidence package excludes source-data files,
contract identifiers, target positions, product- and sector-level PnL attribution,
return time series, event dates, account assumptions, and execution schedules. The
figure builder reads no other research input.

This separation serves two purposes. It prevents accidental disclosure of proprietary
research surfaces, and it makes every public empirical claim auditable against a compact
allowlist. Rounding can create small arithmetic differences between displayed aggregates;
no inference is recomputed from rounded values.

\subsection{Methodology lock}

Before the replication returns were inspected, the following objects were fixed:

\begin{itemize}
  \item causal daily main-contract construction and same-contract returns;
  \item 11-month momentum formation with a one-month skip;
  \item one-month reversal formation;
  \item equal-weight top and bottom 10\% portfolio legs;
  \item a 60-month volatility distribution and fixed Q4 switch;
  \item one-month signal-to-holding lag;
  \item primary lagged open-interest-notional and equal-product market proxies;
  \item prohibition of threshold, sector, product, and universe selection.
\end{itemize}

\subsection{Reproduction of public figures}

The public figures can be rebuilt with the standalone script described in the project
README. The boundary test verifies that the public tree contains no private research
paths, contract-level files, source hashes, or disallowed execution fields, and that the
figure script reads only the aggregate evidence JSON.

\section{Additional Aggregate Tables}

\begin{table}[H]
\centering
\caption{Conditional mean monthly gross returns (percent)}
\begin{tabular}{llrrr}
\toprule
Proxy & State & Months & Momentum & Reversal \\
\midrule
OI-notional & Q1 & 21 & 0.66 & $-0.12$ \\
OI-notional & Q2 & 17 & $-0.92$ & 2.86 \\
OI-notional & Q3 & 14 & 6.04 & $-3.89$ \\
OI-notional & Q4 & 14 & $-0.71$ & $-0.54$ \\
\midrule
Equal product & Q1 & 12 & 5.20 & $-1.97$ \\
Equal product & Q2 & 15 & $-1.07$ & $-1.05$ \\
Equal product & Q3 & 19 & $-1.14$ & 0.29 \\
Equal product & Q4 & 20 & 2.40 & 0.90 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Primary-proxy cross-sectional anatomy by signal state}
\begin{tabular}{lrrr}
\toprule
State & Pairwise correlation & Dispersion & Directional coherence \\
\midrule
Q1 & 0.147 & 1.21\% & 0.300 \\
Q2 & 0.191 & 1.33\% & 0.332 \\
Q3 & 0.187 & 1.50\% & 0.326 \\
Q4 & 0.254 & 1.71\% & 0.376 \\
\bottomrule
\end{tabular}
\end{table}
